%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {West Nile Virus Research Technician} % Job title
    {University of California - Santa Cruz} % Organization
    {Browns Valley, CA} % Location
    {June - Sept. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Conducted mosquito surveys in wetlands, trapping mosquitoes using CDC light traps}
        \item {Identified and sorted mosquito samples for West Nile Virus testing}
        \item {Navigated to sites using GPS devices and maps}
      \end{cvitems}
    }
\medskip
%---------------------------------------------------------
  \cventry
    {Agroforestry Advisor} % Job title
    {Peace Corps} % Organization
    {Guinea, West Africa} % Location
    {Nov. 2011 - Feb. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Planned and implemented water management techniques with a women's gardening cooperative of 2 hectares}
        \item {Reforested 11 hectares of degraded land, collaborating with a local NGO and 51 youth volunteers}
        \item {Organized and co-presented a biodiversity conference, involving over 65 professors, researchers, government agents, and local stakeholders}
        \item {Designed and conducted multiple trainings on various agricultural and natural resource management topics, encompassing over 400 participants}
      \end{cvitems}
    }
\medskip
%---------------------------------------------------------
  \cventry
    {Undergraduate Research Fellow, \textit{Supervisor: Dr. Jonathan Chase, Associate Professor}} % Job title
    {Tyson Research Center, Washington University in St. Louis} % Organization
    {St. Louis, MO} % Location
    {Sep. 2012 - Feb. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Applied for and received a competitive research fellowship to design and conduct an independent research project}
        \item {Conducted pond surveys throughout Missouri, carrying equipment through forested terrain}
        \item {Performed laboratory duties, including identifying and counting aquatic macroinvertebrates and zooplankton and maintaining a species library}
        \item {Active member of laboratory meetings planning future research}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
