%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Presentations}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvitems}
%---------------------------------------------------------
	\bigskip

	\item Evans, Michelle V., RajReni B. Kaul, Courtney C. Murdock, John M. Drake. August 2018. ``What can predictive mapping tell us about the ecology of vector-borne diseases?''. MPE 2013+ Workshop on Global Change and Vector-borne Diseases: Mapping Emerging Infectious Diseases, Fairfax, VA.

	\item Evans, Michelle V., RajReni B. Kaul, Courtney C. Murdock, John M. Drake. February 2018. ``Predicting spatio-temporal dynamics of yellow fever in Brazil''. Population Biology of Vector-borne Diseases Symposium, Athens, GA. \textit{Poster}.

	\item Evans, Michelle V., Lindsey Jones, Nicole Solano, John M. Drake, Courtney C. Murdock. February 2018. ``Mosquito communities across a city''. Odum School of Ecology Graduate Student Symposium, Athens, GA.

	\item Evans, Michelle V., Nicole Solano, Justine Shiau, John M. Drake, Courtney C. Murdock. October 2017. ``Fine-scale microclimate variation across an urban landscape shapes both mosquito population dynamics and arbovirus transmission potential''. Annual Meeting of the Entomological Soceity of America, Denver, CO.

	\item Evans, Michelle V. and Courtney C. Murdock. October 2017. ``Urban microclimate and mosquito dynamics''. Georgia Mosquito Control Association Annual Meeting, Athens, GA.

	\item Evans, Michelle V., Nicole Solano, Justine Shiau, Courtney C. Murdock. August 2017. ``Urban microclimate influences dengue dynamics in the invasive mosquito, \textit{Aedes albopictus}''. Annual Meeting of the Ecological Society of America, Portland, OR.

	\item Evans, Michelle V., Nicole Solano, Justine Shiau, John M. Drake, Courtney C. Murdock. August 2017. ``Urban microclimate and dengue vector competence of the invasive mosquito, \textit{Ae. albopictus}''. VectorBite Research Coordination Network Meeting, London, UK. \textit{Poster.}

	\item Evans, Michelle V. and Courtney C. Murdock. January 2017. ``Microclimate and mosquito-borne disease dynamics''. Odum School of Ecology, Graduate Student Symposium, Athens, GA.

	\item Evans, Michelle V. Nicole Solano, Justine Shiau, Courtney C. Murdock. November 2016. ``Urban microclimate and dengue vector competence of the invasive asian tiger mosquito, \textit{Ae. albopictus}''. Annual Meeting of the American Society of Tropical Medicine and Hygiene. Atlanta, GA. \textit{Poster.}

	\item Evans, Michelle V. and Courtney C. Murdock. October 2016. ``Microclimate and mosquitoes in Athens, GA''. Georgia Mosquito Control Association Annual Meeting, Athens, GA.

	\item Evans, Michelle V., K. Miazgowicz, B. Tesla, Courtney C. Murdock. June 2016. ``Microclimate and mosquitoes across an urban gradient''. Ecology and Evolution of Infectious Disease 14th Annual Meeting, Ithaca, NY. \textit{Poster.}

	\item Evans, Michelle V. and Courtney C. Murdock. February 2016. ``Urbanization and vector-borne disease''. Symposium for Integrative Conservation, Athens, GA.

	\item Evans, Michelle V. and Courtney C. Murdock. January 2016. ``Mosquito dynamics across an urban gradient''. Odum School of Ecology, Graduate Student Symposium, Athens, GA.

	\item Evans, Michelle V., Lauren M. Woods, Jon M. Chase. October 2010. ``The effects of isolation and nutrients on community biomass''. Washington University in St. Louis Undergraduate Research Symposium, St. Louis, MO. \textit{Poster.}

	\item Evans, Michelle V. May 2010. ``Fighting bombs with books: an assessment of the dynamite fishing education program in Ushongo, Tanzania''. School for International Training Symposium, Arusha, Tanzania.

	\bigskip
%---------------------------------------------------------
\end{cvitems}
