%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Selected Presentations}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvitems}
%---------------------------------------------------------
	\bigskip
	\item Evans, Michelle V. February 2019. ``Embracing the complexity of a city to predict dengue hotspots''. Symposium for Integrative Conservation, Athens, GA.

	\item Evans, Michelle V. November 2018. ``Mapping mosquitoes: Using community mapping and OSM to identify disease hotspots''. State of the Map Asia 2018. Bengaluru, India.

	\item Evans, Michelle V., RajReni B. Kaul, Courtney C. Murdock, John M. Drake. August 2018. ``What can predictive mapping tell us about the ecology of vector-borne diseases?''. MPE 2013+ Workshop on Global Change and Vector-borne Diseases: Mapping Emerging Infectious Diseases, Fairfax, VA. \textit{Invited speaker.}

	\item Evans, Michelle V., Nicole Solano, Justine Shiau, John M. Drake, Courtney C. Murdock. October 2017. ``Fine-scale microclimate variation across an urban landscape shapes both mosquito population dynamics and arbovirus transmission potential''. Annual Meeting of the Entomological Society of America, Denver, CO.

	\item Evans, Michelle V. and Courtney C. Murdock. October 2017. ``Urban microclimate and mosquito dynamics''. Georgia Mosquito Control Association Annual Meeting, Athens, GA.

	\item Evans, Michelle V., Nicole Solano, Justine Shiau, Courtney C. Murdock. August 2017. ``Urban microclimate influences dengue dynamics in the invasive mosquito, \textit{Aedes albopictus}''. Annual Meeting of the Ecological Society of America, Portland, OR.

	\item Evans, Michelle V. and Courtney C. Murdock. January 2017. ``Microclimate and mosquito-borne disease dynamics''. Odum School of Ecology, Graduate Student Symposium, Athens, GA.

	\item Evans, Michelle V. Nicole Solano, Justine Shiau, Courtney C. Murdock. November 2016. ``Urban microclimate and dengue vector competence of the invasive Asian tiger mosquito, \textit{Ae. albopictus}''. Annual Meeting of the American Society of Tropical Medicine and Hygiene. Atlanta, GA. \textit{Poster.}

	\item Evans, Michelle V. and Courtney C. Murdock. October 2016. ``Microclimate and mosquitoes in Athens, GA''. Georgia Mosquito Control Association Annual Meeting, Athens, GA.

	\item Evans, Michelle V., K. Miazgowicz, B. Tesla, Courtney C. Murdock. June 2016. ``Microclimate and mosquitoes across an urban gradient''. Ecology and Evolution of Infectious Disease 14th Annual Meeting, Ithaca, NY. \textit{Poster.}

	\item Evans, Michelle V. and Courtney C. Murdock. February 2016. ``Urbanization and vector-borne disease''. Symposium for Integrative Conservation, Athens, GA.

	\item Evans, Michelle V. and Courtney C. Murdock. January 2016. ``Mosquito dynamics across an urban gradient''. Odum School of Ecology, Graduate Student Symposium, Athens, GA.

	\bigskip
%---------------------------------------------------------
\end{cvitems}
